\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2018-08-08 sections/coverpage.tex
Update Coverpage

  \vspace{3.5 cm}
  { \huge \bfseries Correlating Microbial Abundances for the Microbial Interaction Network Database}\\[0.4cm] % Title of your document

@@

  \vspace{1.5 cm}
  Dileep Kishore, Gabriel Birzu, Zhenjun Hu, Charles DeLisi, Kirill Korolev, Daniel Segre\\
  \vspace{1cm}
  Department of XYZ,\\
  The University of ABC\\
  Department of ABC,\\
  XYZ University\\

% DATE SECTION

@@

\vfill % Fill the rest of the page with whitespace

>>>>

  \vspace*{\fill}
  { \huge \bfseries Correlating Microbial Abundances for the Microbial Interaction Network Database}\\[0.4cm] % Title of your document

@@

  % \vspace{1.5 cm}
  % Dileep Kishore\textsuperscript{1},
  % Gabriel Birzu\textsuperscript{2},
  % Zhenjun Hu\textsuperscript{1},
  % Charles DeLisi\textsuperscript{1,3},
  % Kirill Korolev\textsuperscript{1,2},
  % Daniel Segr\`{e}\textsuperscript{1,3,4}\\
  % \vspace{1cm}
  % \textsuperscript{1}Bioinformatics Program, Boston University, Boston, Massachusetts, USA\\
  % \textsuperscript{2}Department of Physics, Boston University, Boston, Massachusetts, USA\\
  % \textsuperscript{3}Department of Biomedical Engineering, Boston University, Boston, Massachusetts, USA\\
  % \textsuperscript{4}Department of Biology, Boston University, Boston, Massachusetts, USA\\

% % DATE SECTION

@@

  \vspace*{\fill} % Fill the rest of the page with whitespace
